A Topic Model of Climate Change Literature

### 2019-12-13 manuscript/coverletter.tex

	\begin{letter}{Bronwyn Wake \\ Chief Editor \\ \textit{Nature Climate Change}}

@@

		\begin{tikzpicture}[remember picture, overlay]
		\node [anchor=south, shift={(-1mm,5mm)}]  at (current page text area.north east) {\includegraphics[width=4cm]{pres/MCC_Logo_RZ_rgb.jpg}
		};
		\end{tikzpicture}

@@

   \opening{\today \\ \\ Dear Bronwyn Wake,}

   I herewith submit on behalf of my co-authors the manuscript ``A Topography of Climate Change Litereature'' for consideration as a letter in Nature Climate Change.

``Big literature'' - the vast and rapidly expanding body of publications - poses new, and largely neglected challenges for climate change assessments and how we understand them. For example, we estimate a total of 350,000 new publications on climate change to emerge (only) in the Web of Science during the Sixth Assessment Cycle of the Intergovernmental Panel on Climate Change spanning from 2015 to 2022. Big data and machine learning methods need to be applied to maintain an overview of developments in the scientific landscape and to analyse how past IPCC assessments have engaged with the available literature. So far, attempts \cite{Bjurström2011, Hulme2010, Victor2015, Kowarsch2017} have often been based on qualitative perceptions, or incomplete data with insufficient methodological sophistication.

In this study we use machine-learning to provide a comprehensive, thematic map of the more than 400,000 articles on climate change published in the Web of Science to date. We perceive two innovations that allow us advance the current state of knowledge on the IPCC and the field it is tasked with assessing. First, our thematic map allows us to situate a complete set of IPCC citations into the context of the wider literature and analyse disciplinary representation adequately.  We find that contrary to previous claims, the social sciences are over-represented in IPCC reports.
Second, the use of machine learning methods in creating the map allows us to analyse the content of publications more or less represented in the IPCC. We find that literature on technical solutions (such as negative emissions, buildings or cities) is growing fast and, even compared to other fast-growing literatures, has been under-represented in IPCC reports. We point towards a variety of other applications of such a comprehensive, thematic literature map within global environmetal assessments as well as the broad field of research synthesis. Our findings have direct implications for addressing growing demands for more solution-oriented climate change assessments that are also more firmly rooted in the social sciences.

@@

\bibliography{Mendeley}
\bibliographystyle{unsrt}

>>>>

	\begin{letter}{Adam Yeeles \\ Editor \\ \textit{Nature Climate Change}}

@@

		\begin{tikzpicture}[remember picture, overlay]
		\node [anchor=south, shift={(-1mm,5mm)}]  at (current page text area.north east) {\includegraphics[width=4cm]{../pres/MCC_Logo_RZ_rgb.jpg}
		};
		\end{tikzpicture}

@@

   \opening{\today \\ \\ Dear Adam Yeeles,}

   I herewith resubmit on behalf of my co-authors the Letter ``A Topography of Climate Change Literature'' (NCLIM-19071401).

   The letter made use of topic modelling in order to reassess claims made in the literature about how the IPCC has represented scientific knowledge about climate change. This in the context of Big Literature - the hundreds of thousands of papers published on climate change which it is the IPCC's job to assess.

   We express our gratitude for the handling of our manuscript, and for the comments received from the reviewers. We have edited our manuscript accordingly and attach a point by point response to all comments.
   The comments received were clear and along similar lines. Broadly speaking, we 
   \begin{itemize}
   	\item Improved the clarity of our description of our methods in the main text so that they could be understood by a non-specialist audience.
   	\item Added significant nuance to the interpretation of our results. We have been more explicit about what can and can't be drawn as recommendations from our analysis, given its advantages and drawbacks. This has led in turn to a more interesting discussion about how the methods we propose could be used in further IPCC assessments.
   \end{itemize}

	We are confident that this re-submission addresses all of the concerns raised by the reviewers.

@@

\section{Manuscript details}

\begin{tabular}{l r r}

	 & \textbf{Main text} & \textbf{SI \& Methods} \\
	 \textbf{Words} & 2196 & 1584 \\
	 \textbf{Figures} & 4 & 5 \\
	 \textbf{Tables} & 1 & 1 \\
	 \textbf{References} & 19 & 12

\end{tabular} 
%\bibliography{Mendeley}
%\bibliographystyle{unsrt}
